D3064R0: OOTA Execution is Provably Vacuous

### 2023-12-01 ootavacuous.tex
Note that tools do not currently flag all OOTA cycles
Reported-by: Jade Alglave <Jade.Alglave@arm.com>
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Some executable C++ memory models correctly flagged executions involving
OOTA~\cite{JadeAlglave2014HerdingCats}.\footnote{
	Others cleverly avoid this issue by forbidding atomic
	stores of non-constant values~\cite{MarkBatty2011cppmem}.}
% @@@ Better herd7 C11 citation?
However, because these models are atemporal, they cannot reject
OOTA executions other than by flagging the OOTA value as arbitrary
(which some in fact do).

>>>>

Some executable C++ memory models correctly flagged executions involving
OOTA~\cite{JadeAlglave2014HerdingCats}.\footnote{
	Others cleverly avoid this issue by forbidding atomic
	stores of non-constant values~\cite{MarkBatty2011cppmem}.}
% @@@ Better herd7 C11 citation?
However, because these models are atemporal, they cannot reject
OOTA executions other than by flagging the OOTA value as arbitrary
(which some in fact do in at least some cases).
